---
title: 'Mini-Tutorial for RPushbullet'
subtitle: 'How to Set Up Remote Error Catching with R Scripts'
author: 'Anthony Raborn, Univeristy of Florida'
output: rmarkdown::github_document
---

#### Last updated on `r format(Sys.Date(), "%B %d, %Y")`.

# R Script for installing/using RPushbullet

Make sure you have the Pushbullet app (phone) and/or the Pushbullet extension (browser) set up in order to use this. Go to: www.pushbullet.com and sign up first!         

Here is a quick function I use to make sure that RPushbullet is installed on a computer before my script is run.

```{r install function}
is.installed <- function(mypkg){
  is.element(mypkg, installed.packages()[,1])
} 
```
 
Using the function forces the installation of the `RPushbullet` package.

```{r try the function out}
if (!is.installed("RPushbullet")){
  install.packages("RPushbullet")
}
```

Change the default error options in R to use RPushbullet to forward your errors to all your connected devices. (This Can be reset by calling `options(error = NULL)`!)

```{r set rpushbullet error}
options(error = function() { 
  RPushbullet::pbPost("note", "Error", geterrmessage())
  if(!interactive()) stop(geterrmessage())
})
```
 
What this does is send you a Pushbullet notification whenever your R script hits an error. However, it *will not* be able to tell you if a power outage, inconsiderate student, or terribly-planned update stopped the simulation without warning.

```{r load RPushbullet}
library(RPushbullet)
```

Check for the warning message `"No file ~/.rpushbullet.json found"`. If this pops up, you need to find the default or home directory of the computer (the `"~/"` directory) by calling `dirname("~/")`. This is where your .json file gets placed.

However, that means you need to create the ".rpushbullet.json" file. The `Rpushbullet` package can help with that:

```{r create json file, eval=F}
pbSetup(apikey = "youraccesstoken")
```

This will create the .json file for you in your home directory (again, in `"~/"`). The api key can be found by logging into your Pushbullet account that you created earlier, going to https://www.pushbullet.com#settings, and clicking on "Create Access Token". Then, you can paste the access token in place of "youraccesstoken" and have your .json file created automatically!

Then, all you need to do (in addition to appending the code above, **except** the `pbSetup()` function, into your R script) is remember to move the .rpushbullet.json file into the home directory of the computer(s) you're using for your scripts.

If you need any more detailed help, look at the `RPushbullet` help files and the package author's page: https://github.com/eddelbuettel/rpushbullet.

# Copy of Code to Include in the Beginning of your R Scripts

```{r}
is.installed <- function(mypkg){
  is.element(mypkg, installed.packages()[,1])
} 
if (!is.installed("RPushbullet")){
  install.packages("RPushbullet")
}
options(error = function() { 
  RPushbullet::pbPost("note", "Error", geterrmessage())
  if(!interactive()) stop(geterrmessage())
})
library(RPushbullet)
```